\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Development Engineer Intern}
    {TELUS Health}
    {Toronto, ON}
    {May. 2020 - Aug. 2020}
    {
      \begin{cvitems}
        \item {Containerized the Data Warehouse Connector project for widespread use within company.}
        \item {Built Jenkins CI/CD pipelines with Bitbucket hooks for multiple projects.}
        \item {Deployed MongoDB Charts for EMR data visualization regarding different health statistics.}
        \item {Built internal CLI tooling allowing developers to deploy Docker stacks with Mirth and MongoDB instances on company servers.}
      \end{cvitems}
    }
  \cventry
    {DevOps Engineer Intern}
    {Ultimate Software}
    {Toronto, ON}
    {Sep. 2019 - Dec. 2019}
    {
      \begin{cvitems}
        \item {Led the containerization project to convert company product applications into Docker containers, reducing resource cost by 50\%.}
        \item {Designed and built internal tooling for developers to build development clusters locally through Docker.}
        \item {Optimized project build pipelines on TeamCity to use less resources and speed up build times by 20\%.}
      \end{cvitems}
    }
  \cventry
    {DevOps Engineer Intern}
    {Tulip Retail}
    {Toronto, ON}
    {Jan. 2019 - Apr. 2019}
    {
      \begin{cvitems}
        \item {Implemented a multitude of monitors and metrics within Datadog and AWS CloudWatch to monitor project infrastructure.}
        \item {Configured Cloudflare DNS to enable communication between devices in China and servers in North America.}
        \item {Containerized Ops-specific tooling for widespread use within company with ample documentation in runbooks.}
        \item {Ported all company projects for continuous delivery from Jenkins CI to GitLab CI.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer Intern}
    {Grapevine6}
    {Toronto, ON}
    {May. 2018 - Aug. 2018}
    {
      \begin{cvitems}
        \item {Improved codebase efficiency and reduced database call times by 33\%.}
        \item {Implemented key mobile and desktop features for high-profile clients.}
        \item {Added thorough Swagger integration tests to the codebase's backend API endpoints.}
        \item {Assisted in adding a multitude of news sources for content aggregation with company application.}
      \end{cvitems}
    }
  \cventry
    {Software Developer Intern}
    {Espresso Capital}
    {Toronto, ON}
    {Sep. 2017 - Dec. 2017}
    {
      \begin{cvitems}
        \item {Merged company's borrower portal's AngularJS frontend with its Django REST Framework backend.}
        \item {Reduced borrower portal's API call response time by 80\%.}
        \item {Created numerous regression testing suites for borrower portal with Postman and Selenium.}
        \item {Integrated Sage One services to the borrower portal's second phase.}
        \item {Moved borrower portal's first phase to production environment.}
        \item {Ported the company's machine-learning risk model server from Flask to Django.}
      \end{cvitems}
    }
\end{cventries}
